Insert Title

### 2017-01-24 paper/main.tex
More updates to the paper

@@

Ultimately the upsides of the 2D array based method won out, with the main choice being influenced by the computational efficiency, as well as the visualization. The visualization was distinctly important, as it allowed us to understand and debug the model as needed.

@@

Before considering statistics, consider Figure \ref{fig:5By5}. This is a visualization of our model and shows the structure of the world space which the cars live in. As you can see here, the cars in this simulation live somewhere with no lanes ended. Other figures you will be able to see the shape of where the cars live, as well as approximately the density.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.15]{Images/55_ez.png}
\caption{Travel times for L = 5, B = 5 baseline case for automated tollbooths. Mean is 23.4 seconds. }
\label{fig:ez55}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.15]{Images/55_man.png}
\caption{Travel times for the L = 5, B = 5 baseline case for manual tollbooths. Mean is 22.5 seconds.}
\label{fig:manual55}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{Images/3By8LeftOne.png}
\end{center}
\caption{The image represents traffic flow from 8 tollbooths into 3 highway lanes from top to bottom. }
\label{fig:3By8RightTri}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.3]{Images/hist_3_8.png}
\caption{A histogram showing the travel times for B = 8, L = 3. The delay times are relative to the benchmark for all manual tollbooths. Mean is 21.0 seconds.}
\label{fig:manual38}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{c c}
\includegraphics[scale=0.25]{Images/4By8MidTriOne.png} & \includegraphics[scale=0.25]{Images/4By8MidTriTwo.png}
\end{tabular}
\end{center}
\caption{The two images represent traffic flow from eight tollbooths into four traffic lanes, where the image on the right is one time step ahead of the image on the right. Where the cars stop appearing is where the traffic lane ends. }
\label{fig:48_split}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.32]{Images/DoubleWhiteLines.png}
\end{center}
\caption{The image represents traffic flow from 8 tollbooths to 4 lanes with double white lines in place. The double white lines are represented by the bold black lines in the image. }
\label{fig:merge_patterns}
\end{figure}
% Isaac, put the graph with the double white lines here. label merge_patterns
% Add something about how the double white lines are thick black instead for visibility
% Make it an H so it is right here.

@@

Finally, we were unable to definitively determine the reason that cars were able to travel faster in structures where B=L than in structures where B $<$L. This was counter to what we expected, but we suspect the reason is that each of our road designs would have a different capacity, or critical density. This would change the relationship between throughput and travel time. Given more time, we would have liked to identi 
\subsection{Final Recommendation}
\label{final_rec}

>>>>

\usepackage[margin=1.5in]{geometry}

@@

Ultimately the upsides of the 2D array based method won out, with the main choice being influenced by the computational efficiency, as well as the visualization. The visualization was distinctly important, as it allowed us to understand and debug the model as needed. Additionally, the use of a 2D array allowed us to define the distance between lattices as approximately 15 feet, and each timestep to have a length of 1 second. This means that high way speeds of 60 miles an hour corresponds to 6 units forward per second. Therefore our model allows for the cars to reach highway speeds.

@@

Before considering statistics, consider Figure \ref{fig:5By5}. This is a visualization of our model and shows the structure of the world space which the cars live in. As you can see here, the cars in this simulation live somewhere with no lanes ended. In other figures, you will be able to see the shape of where the cars live, as well as approximately the density.

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{Images/55_ez.png}
\caption{Travel times for L = 5, B = 5 baseline case for automated tollbooths. Mean is 23.4 seconds. }
\label{fig:ez55}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.25]{Images/55_man.png}
\caption{Travel times for the L = 5, B = 5 baseline case for manual tollbooths. Mean is 22.5 seconds.}
\label{fig:manual55}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.203]{Images/3By8LeftOne.png}
\end{center}
\caption{The image represents traffic flow from 8 tollbooths into 3 highway lanes from top to bottom. }
\label{fig:3By8RightTri}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Images/hist_3_8.png}
\caption{A histogram showing the travel times for B = 8, L = 3. The delay times are relative to the benchmark for all manual tollbooths. Mean is 21.0 seconds.}
\label{fig:manual38}
\end{center}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\begin{tabular}{c c}
\includegraphics[scale=0.23]{Images/4By8MidTriOne.png} & \includegraphics[scale=0.23]{Images/4By8MidTriTwo.png}
\end{tabular}
\end{center}
\caption{The two images represent traffic flow from eight tollbooths into four traffic lanes, where the image on the right is one time step ahead of the image on the right. Where the cars stop appearing is where the traffic lane ends. }
\label{fig:48_split}
\end{figure}

@@

\begin{figure}[H]
\begin{center}
\includegraphics[scale=0.27]{Images/DoubleWhiteLines.png}
\end{center}
\caption{The image represents traffic flow from 8 tollbooths to 4 lanes with double white lines in place. The double white lines are represented by the bold black lines in the image. }
\label{fig:merge_patterns}
\end{figure}
% Isaac, put the graph with the double white lines here. label merge_patterns
% Add something about how the double white lines are thick black instead for visibility
% Make it an H so it is right here.

@@

Finally, we were unable to definitively determine the reason that cars were able to travel faster in structures where B=L than in structures where B $<$L. This was counter to what we expected, but we suspect the reason is that each of our road designs would have a different capacity, or critical density. This would change the relationship between throughput and travel time. Given more time, we would have liked to identify the critical density of our designs, but this optimization would have required many more simulations than we could achieve in a short time.  
\subsection{Final Recommendation}
\label{final_rec}
